\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-02-04 pdbf-doc.tex
sync README and pdbf-doc

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) and a LaTeX distribution installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile minimal.tex file with this command: \texttt{java -jar pdbf.jar minimal.tex}
\item Open minimal.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --vm minimal.html vldb-Invaders.ova}.
\item Open minimal.ova, this is the final output with the attached ova file. Its still a valid pdf and html at the same time.
\item You can play around with the minimal.tex file. It contains a small example on how to specify PDBF elements in LaTeX
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\section{How to use the PDBF compiler}
Right now there are only three modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the tex file and has the same name as the tex file but ".html" as filename extension.\\[8pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|\\[2pt]
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .ova files!
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".ova" as filename extension.
-- The TAR mode which attaches a tar archive file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --tar PDBF_File.html TAR_File.tar|\\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".tar" as filename extension.
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .tar files!

>>>>

\section{Getting started}
\subsection{Normal usage}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) and a LaTeX distribution installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile minimal.tex file with this command: \texttt{java -jar pdbf.jar minimal.tex}
\item Open minimal.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\end{itemize}
\subsection{Attach a VirtualBox image}
\begin{itemize}
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --vm minimal.html vldb-Invaders.ova}.
\item Open minimal.ova, this is the final output with the attached ova file. Its still a valid pdf and html file at the same time.
\end{itemize}
\subsection{Attach a tar archive}
\begin{itemize}
\item Optionally you can attach a tar archive file to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --tar minimal.html TAR\_file.tar}
\item Open minimal.tar, this is the final output with the attached tar file. Its still a valid pdf and html file at the same time.
\end{itemize}
\subsection{Learn how to use the PDBF framework}
\begin{itemize}
\item You can play around with the minimal.tex file. It contains a small example on how to specify PDBF elements in LaTeX
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\section{How to use the PDBF compiler}
Right now there are only three modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the tex file and has the same name as the tex file but ".html" as filename extension.\\[8pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|\\[2pt]
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .ova files!
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".ova" as filename extension.\\[8pt]
-- The TAR mode which attaches a tar archive file to an existing PDBF document:\\
\verb|java -jar PDBF.jar --tar PDBF_File.html TAR_File.tar|\\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".tar" as filename extension.
\textbf{Note:} Currently there is a hard size limit of 1.9GB for .tar files!
